Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-11 preliminaries.tex
Deal with another couple action items

\begin{definition} [$\SampBQP$]
	$\SampBQP$ is the class of sampling problems $S=\left(D_x\right)_{x\in\set{0, 1}^*}$ for which there exists a polynomial-time quantum algorithm $B$ that, given $(x, 0^{1/\varepsilon})$ as input, samples from a probability distribution $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
\end{definition}

@@

\begin{definition}
	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and computational soundness \Ethan{Specify it's computational or no?} if for all $x\in\zo^*$:
	\begin{itemize}
		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
		\item Let $(d, z)\leftarrow(P, V)(x, 1^{1/\varepsilon}, 1^\lambda)$, then $d=\Rej$ with probability at most $c(\lambda)$.
		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
			Define $z_{ideal}$ by
			$$\begin{cases}
				z_{ideal}=\bot & \text{if } d=\Rej\\
				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
			\end{cases}$$
			then for all adversary, its probability to distinguish a sample of $(d, z)$ from that of $(d, z_{ideal})$ is less than $\varepsilon$.
	\end{itemize} \hannote{need computational version of soundness?} \Ethan{Yeah. Will fix.}
\end{definition}

@@

\begin{thm}
	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on some Hilbert space $\cH=\cS+\cS^\bot$.
	The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
	$$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}^2}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
\end{thm}

@@

\Ethan{State the one below; prove the one above in appendix}

\begin{thm}
	\label{thm:projection}
	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
	$$J=\frac{10\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
	then we have
	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
\end{thm}

>>>>

\begin{definition} [$\SampBQP$]
	$\SampBQP$ is the class of sampling problems $S=\left(D_x\right)_{x\in\set{0, 1}^*}$ for which there exists a polynomial-time quantum algorithm $B$ that, given $(x, 1^{1/\varepsilon})$ as input, samples from a probability distribution $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
\end{definition}

@@

\begin{definition}
	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
	We say $\Pi$ is a computationally sound protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
	\begin{itemize}
		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
		\item Let $(d, z)\leftarrow(P, V)(x, 1^{1/\varepsilon}, 1^\lambda)$, then $d=\Rej$ with probability at most $c(\lambda)$.
		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
			Define $z_{ideal}$ by
			$$\begin{cases}
				z_{ideal}=\bot & \text{if } d=\Rej\\
				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
			\end{cases}$$
			then for all adversary, its probability to successfully distinguish a sample of $(d, z)$ from that of $(d, z_{ideal})$ is less than $\frac{1}{2}+\frac{\varepsilon}{2}$
			\Ethan{Something like this? Or need protocol or specify prior probability is 1/2 each?}
	\end{itemize}
\end{definition}

@@

\begin{thm}
	\label{thm:proj1}
	Let $H=H_1+H_2$ be the sum of two Hamiltonians operating on some Hilbert space $\cH=\cS+\cS^\bot$.
	The Hamiltonian $H_2$ is such that $\cS$ is a zero eigenspace and the eigenvectors in $\cS^\bot$ have eigenvalues at least $J>2\norm{H_1}$. Then,
	$$\lambda\left(H_1\big|_\cS\right)-\frac{\norm{H_1}^2}{J-2\norm{H_1}^2}\leq\lambda(H)\leq\lambda\left(H_1\big|_\cS\right)$$
\end{thm}

@@

\begin{thm}
	\label{thm:projection}
	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
	$$J=\frac{11\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
	then we have
	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
\end{thm}
\begin{proof}
	Apply \Cref{thm:proj1} to $H=H_1+JH_2$. Note that the least nonzero eigenvalue of $JH_2$ is greater than $10\norm{H_1}$.
\end{proof}
